### 2021-07-25 paper.tex
results in toc was Result instead of result, changed that
appendix added, code implementation using tensorflow done
fast.ai implementation added
Background separted, added cnn result and code
Background is now in separte file

Code for CNN has been added and predictions for fast.ai

two differnent prediction images

cnn's comparsion graph added too.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}

% font
\usepackage{tgschola}
\usepackage{amsmath}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

% bibliography
\usepackage{url}
\usepackage[
	backend=biber,
	style=numeric,
	%citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

\usepackage{wrapfig}

% table of content name
\addto\captionsenglish{% Replace "english" with the language you use
	\renewcommand{\contentsname}%
	{\hfill \Huge Table of Content \hfill}%
}

@@

	\section[background]{Background}

	Natarajan \cite{bac1} proposed brain tumor detection method for MRI brain
	images. The MRI brain images are first preprocessed using median filter,
	then segmentation of image is done using threshold segmentation and
	morphological operations are applied and then finally, the tumor region is
	obtained using image subtraction technique. This approach gives the exact
	shape of tumor in MRI brain image. Joshi \cite{bac2}  proposed brain tumor
	detection and classification system in MR images by first extracting the
	tumor portion from brain image, then extracting the texture features of the
	detected tumor using Gray Level Co- occurrence Matrix (GLCM) and then
	classified using neuro-fuzzy classifier. Amin and Mageed \cite{bac3}
	proposed neural network and segmentation base system to automatically detect
	the tumor in brain MRI images. The Principal Component Analysis (PCA) is
	used for feature extraction and then Multi-Layer Perceptron (MLP) is used
	classify the extracted features of MRI brain image.  The average recognition
	rate is 88.2\% and peak recognition rate is 96.7\%.  Sapra \cite{bac4}
	proposed image segmentation technique to detect brain tumor from MRI images
	and then Probabilistic Neural Network (PNN)  is used for automated brain
	tumor classification in MRI scans. PNN system proposed handle the process of
	brain tumor classification more accurately. Suchita and Lalit \cite{bac5}
	proposed unsupervised neural network learning technique for classification
	of brain MRI images.  The MRI brain images are first preprocessed which
	include noise filtering, edge detection, then the tumor is extracted using
	segmentation. The texture features are extracted using Gray-Level
	Co-occurrence Matrix(GLCM) and then Self-Organizing Maps (SOM) are used to
	classify the brain as normal or abnormal brain, that is, whether it contain
	tumor or not. Rajeshwari and Sharmila \cite{bac6} proposed preprocessing
	techniques which are used to improve the quality of MRI image before using
	it into an application. The average, median and wiener filters are used for
	noise removal and interpolation based Discrete Wavelet Transform (DWT)
	technique is used for resolution enhancement. The Peak Signal to Noise Ratio
	(PSNR) is used for evaluation of these techniques.

@@

	\section{Result}%
	\label{sec:result}

@@

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\linewidth]{imgs/result.png}
		\caption{Predictions made by the VGG16 model in tensorflow on random data}%
		\label{fig:result}
	\end{figure}

	As it can be seen from Figure~\ref{fig:result} there are some false
	positives in our predictions.

>>>>

% fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{tgschola}
\usepackage{inconsolata}
\usepackage{amsmath}

% images
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{wrapfig}

% code listing
\usepackage{minted}
\usemintedstyle{tango}

@@

% bibliography
\usepackage{bookmark}
\usepackage{url}
\usepackage[
	backend=biber,
	style=numeric,
	%citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

% table of content name
%\usepackage[nottoc]{tocbibind}
%\renewcommand{\theHsection}{\thepart.section.\thesection}
%\addto\captionsenglish{% Replace "english" with the language you use
	%\renewcommand{\contentsname}%
	%{\hfill \Huge Table of Content \hfill}%
%}

@@

	\section[background]{Background}
	\input{backgournd.tex}

@@

	\section[result]{Result}%
	\label{sec:result}

@@

	\begin{figure}[H]
		\centering
		\subfloat[cnn using tensorflow]
		{\includegraphics[width=0.4\linewidth]
		{imgs/tf_cnn.png}\label{tf_cnn_cmp}}
		\hspace{0.5cm}
		\subfloat[cnn using fast.ai]
		{\includegraphics[width=0.5\linewidth]
		{imgs/fastai_cnn.png}\label{fastai_vgg16_cmp}}
		\caption{CNN implemented in fast.ai and tensorflow}
		\label{CNN in fast.ai and tensorflow}
	\end{figure}

@@

	\begin{figure}[H]
		\centering
		\subfloat[prediction made by VGG16 implemented in tensorflow]
		{\includegraphics[width=0.5\linewidth]
		{imgs/result.png}\label{vgg16_tf}}
		\hspace{0.3cm}
		\subfloat[prediction made by ResNet50 implemented in fast.ai]
		{\includegraphics[width=0.5\linewidth]
		{imgs/result_fast_ai.png}\label{resnet_fastai}}
		\caption{Comparing Predictions made by models}
		\label{fig:Results_Comparison}
	\end{figure}

	As it can be seen from Figure~\ref{fig:Results_Comparison} there are some false
	positives in our predictions.

	\section[appendix]{Appendix}%
	\label{sec:Appendix}

	\subsection{Tensorflow Implementation}%
	\label{sub:Tensorflow Implementation}

	\subsubsection{CNN}
	\input{tf_cnn.tex}

	\subsubsection{VGG 16}
	\input{tf_vgg.tex}

	\subsubsection{ResNet 50}
	\input{tf_reset.tex}

	\subsubsection{Prediction}
	\input{tf_prediction.tex}

	\subsection{fast.ai Implementation}%
	\label{sub:fast.ai Implementation}

	\subsubsection{CNN}
	\input{fastai_cnn.tex}

	\textbf{Prediction}
	\input{fastai_cnn_pred.tex}

	\subsubsection{VGG 16}
	\input{fastai_vgg.tex}

	\textbf{Prediction}
	\input{fastai_vgg_pred.tex}

	\subsubsection{ResNet 50}
	\input{fastai_resnet.tex}

	\textbf{Prediction}
	\input{fastai_resnet_pred.tex}
